% Executive Summary - One Page Version
\vspace{0.3cm}
\begin{center}
\textcolor{fabPrimary}{\Large\textbf{Building the Future of Smart Device Creation}}
\end{center}

\vspace{0.2cm}
\noindent !Forge democratizes smart device creation through AI and blockchain technology. Our platform transforms ideas into physical reality without requiring engineering expertise, opening the \$500B+ smart device market to everyone.

\vspace{0.2cm}
\begin{multicols}{2}
\textcolor{fabPrimary}{\textbf{Our Mission}}\\
\noindent To eliminate barriers in hardware creation by providing an intuitive, AI-guided process that anyone can use to build custom smart devices—from drones to automated systems.

\columnbreak

\textcolor{fabPrimary}{\textbf{Market Opportunity}}\\
\noindent \$500B+ smart device market (2025) with 15-30\% growth across IoT sectors. Rising demand for customized devices and growth of maker movement.
\end{multicols}

\vspace{0.2cm}
\begin{multicols}{2}
\textcolor{fabSecondary}{\textbf{Key Platform Features}}
\vspace{0.05cm}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt]
    \item AI-guided component selection
    \item Automated code generation
    \item 3D modeling optimization
    \item Decentralized marketplace
    \item Local manufacturing network
\end{itemize}

\columnbreak

\textcolor{fabAccent}{\textbf{Competitive Edge}}
\vspace{0.05cm}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt]
    \item End-to-End Solution: Concept to finished device
    \item AI Integration: Simplifies complex processes
    \item Blockchain Utility: Deflationary token mechanics
    \item Network Effects: Value grows with ecosystem
\end{itemize}
\end{multicols}

\vspace{0.2cm}
\begin{center}
\begin{minipage}{0.95\textwidth}
\textcolor{fabSecondary}{\textbf{FRGE Token Ecosystem}}
\end{minipage}
\end{center}

\vspace{0.05cm}
\noindent Our two-tier system offers free users data monetization while premium users pay for privacy. 20\% of subscription revenue buys and burns FRGE tokens, creating deflationary pressure. Marketplace transactions in FRGE enjoy reduced fees (5\% vs 15\% for FIAT), with all FRGE fees burned.

\vspace{0.2cm}
\begin{multicols}{3}
\textcolor{fabPrimary}{\textbf{Token Utility}}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt]
    \item Project investment
    \item Data monetization
    \item Marketplace purchases
    \item Professional services
\end{itemize}

\columnbreak

\textcolor{fabSecondary}{\textbf{Distribution}}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt]
    \item Investors: 40\%
    \item Team: 20\%
    \item Ecosystem: 20\%
    \item Liquidity: 20\%
\end{itemize}

\columnbreak

\textcolor{fabAccent}{\textbf{Economics}}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt]
    \item Total Supply: 100M FRGE
    \item Deflationary model
    \item 20\% of FIAT buys \& burns
    \item All fees burn FRGE
\end{itemize}
\end{multicols}

\vspace{0.2cm}
\noindent The !Forge platform uniquely combines AI, blockchain, and manufacturing to democratize creation capabilities previously available only to large companies and experienced engineers, while establishing a sustainable ecosystem for all participants. 